Computational Documents

### 2019-12-27 cd_compendium.Rmd
start small,but most useful

@@

>>>>

# 시작점 {#inception}

Robert Gentleman과 Duncan Temple Lang이 2004년 발표한 논문에서 공식적인 시작점을 찾을 수 있다.[^duncan] [^robert]

[^duncan]: "Statistical Analyses and Reproducible Research" Bioconductor Project Working Papers
[^robert]: "Reproducible Research: A Bioinformatics Case Study" in Statistical Applications in Genetics and Molecular Biology

> We introduce the concept of a compendium as both a container for the different elements that make up the 
> document and its computations (i.e. text, code, data,...), and as a means for distributing, managing and 
> updating the collection. - Gentleman, R. and Temple Lang, D. (2004)

@@

# 시작이 반이다 {#start-small}
